Supplementary Materials: Constructing Statistical Deformable Models with Shape Flow

### 2015-04-29 supplementary.tex
year fix, figure -> eps

\begin{figure}[!t]
    \centering
    \begin{subfigure}[b]{0.4\textwidth}
            \includegraphics[width=\textwidth]{supports/Model_Analysis/variance_ratio}
        %\caption{dAAMs vs AAMs Variance Ratio}
    \end{subfigure}
    \begin{subfigure}[b]{0.4\textwidth}
            \includegraphics[width=\textwidth]{supports/Model_Analysis/cumulative_variance_ratio}
        %\caption{dAAMs vs AAMs Cumulative Variance Ratio}
    \end{subfigure}
    \caption{dAAMs vs AAMs Variance Ratios}
    \label{fig:compact}
\end{figure}

>>>>

\begin{figure}[!t]
    \centering
    \begin{subfigure}[b]{0.4\textwidth}
            \includegraphics[width=\textwidth]{supports/Model_Analysis/var_ratio}
        %\caption{dAAMs vs AAMs Variance Ratio}
    \end{subfigure}
    \begin{subfigure}[b]{0.4\textwidth}
            \includegraphics[width=\textwidth]{supports/Model_Analysis/cumu_var_ratio}
        %\caption{dAAMs vs AAMs Cumulative Variance Ratio}
    \end{subfigure}
    \caption{dAAMs vs AAMs Variance Ratios}
    \label{fig:compact}
\end{figure}
